Cartograms with Dynamic Features

### 2022-10-11 paper/section/evaluation.tex
feat: add evaluation draft

We recruited X participants, [add demographics here].

@@

Datasets are projected on a map that consists of 135 CGGs in England.

\subsection{Tasks}

We conducted tasks to evaluate the effectiveness of our approach.

\textbf{T1:} The participants were asked to familiarize themselves with the design, including the user options and the interaction methods.
\textbf{T2:} The participants

\subsection{Questionnaire}

We asked participants to complete a questionnaire to collect their feedback. The questionnaire consisted of the following questions:

\begin{itemize}
    \item \dots
    \item \dots
\end{itemize}

>>>>

We recruited X participants, [add demographic analysis here].

@@

135 CGGs are projected on the screen with a choropleth, we then generated another view with our visual design. The color in both visualizations are mapped to population. See \autoref{fig:task}.

{
    \begin{figure}[tb!]
        \centering
        \includegraphics[width=\columnwidth,keepaspectratio]{figure/evaluation/task.png}
        \caption{A typical task for participants. The left shows the choropleth map, and the right shows the cartogram. Both visualizations show the three longest rivers in England, and the color is mapped to CCG population. The target CGG will be blinking on the choropleth (shown in black), participants are asked to identify this CCG on the cartogram.}
        \label{fig:task}
    \end{figure}
}

\subsection{User Experiment}

We conducted a user experiment to evaluate the effectiveness of our approach. The experiment was designed to be conducted remotely, and participants were asked to complete the tasks on their own computers. The experiment includes four parts:

\textbf{P1:} The participants were asked read instructions and trainings provided in both text and videos. The instructions were designed to help participants understand the concepts used in the tasks. Videos are available at \url{https://www.youtu.be/playlist?list=PLL7sHvxLtD75fMtrUQrAdddjt3wfFkcWz}.

\textbf{P2:} The participants were given three practice tasks to familiarize themselves with the experiment. A demonstration of the task is also included in the instructional video.

\textbf{P3:} The participants were asked to complete 16 location tasks. The response and reaction time are recorded. These 16 CCGs were carefully selected to avoid extreme cases (thus biases the result), in terms of size, color, and location.

\textbf{P4:} The participants were asked to complete a questionnaire that consists of Likert Scale questions and open-ended questions.

The user experiment is available at \url{https://osf.io/q39w7}.

### 2022-10-11 paper/section/main.tex
fix: typos
feat: add evaluation draft

 {
  \begin{figure}[tb!]
      \centering
      \includegraphics[width=\columnwidth,keepaspectratio]{example-image-a}
      \caption{An screenshot of \software. Figure TBA.}
      \label{fig:overview}
  \end{figure}
 }

 {
  \begin{figure*}[tb!]
      \centering
      \includegraphics[width=\textwidth,height=0.95\textheight,keepaspectratio]{figure/flowchart.png}
      \caption{A flowchart illustration of our layout algorithm. See \autoref{fig:flowchart-stalemate} for the flow of processing stalemate. See also \autoref{alg:UpdateLayout} for more detail. For illustration purposes, we show the rendered views alongside the logical views representing the actual computation.}
      \label{fig:flowchart}
  \end{figure*}

  \begin{figure}[tb!]
      \centering
      \includegraphics[width=0.9\columnwidth,keepaspectratio]{figure/flowchart stalemate.png}
      \caption{A flowchart illustration of stalemate processing.}
      \label{fig:flowchart-stalemate}
  \end{figure}
 }

@@

We use rivers as topological boundaries and prevent nodes from crossing them. The resolution of rivers can be adjusted by the user, as shown in \autoref{fig:river resolution}, the number of vertices is reduced from 10,170 to 30. A pixel-level river resolution is not required as Demers cartograms do not need to represent geography at this level of detail. Instead a resolution that matches the node size is used. Enabling river simplification reduces the number of edge intersection tests that need to be performed. When a node's position changes, we test if the node's trajectory intersects any segment of a river. See \autoref{alg:check river intersection}. A bounding box intersection test between the edge defined by node translation and river edges can be performed to reduce the number of edge intersection tests required.

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/stalemate.png}
            \caption{A stalemate situation is when a node's translation path $ \nodeVectorCT $ (in iteration 1) intersects a river $ \stalemateMax $ times. The node is translated back to its previous position (iteration 2). A stalemate often occurs when the area is congested and the node is unable to translate to a new position without intersecting a river.}
            \label{fig:stalemate}
        \end{figure}
    }

>>>>

 {
  \begin{figure}[tb!]
      \centering
      \includegraphics[width=\columnwidth,keepaspectratio]{figure/UI.png}
      \caption{An screenshot of \software. User options are provided to adjust the size, color mapping, visibility of nodes and rivers. Other options include the ability to control the overlap removal behavior: rivers can be static, dynamic, or constrained.}
      \label{fig:overview}
  \end{figure}
 }

 {
  \begin{figure*}[tb!]
      \centering
      \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figure/flowchart.png}
      \caption{A flowchart illustration of our layout algorithm. See \autoref{fig:flowchart-stalemate} for the flow of processing stalemate. See also \autoref{alg:UpdateLayout} for more detail. For illustration purposes, we show the rendered views alongside the logical views representing the actual computation.}
      \label{fig:flowchart}
  \end{figure*}

  \begin{figure}[tb!]
      \centering
      \includegraphics[width=\columnwidth,keepaspectratio]{figure/flowchart stalemate.png}
      \caption{A flowchart illustration of stalemate processing.}
      \label{fig:flowchart-stalemate}
  \end{figure}
 }

@@

We use rivers as topological boundaries and prevent nodes from crossing them. The resolution of rivers can be adjusted by the user, as shown in \autoref{fig:river resolution}, the number of vertices is reduced from 10,170 to 30. A pixel-level river resolution is not required as Demers cartograms do not need to represent geography at this level of detail. Instead, a resolution that matches the node size is used. Enabling river simplification reduces the number of edge intersection tests that need to be performed. When a node's position changes, we test if the node's trajectory intersects any segment of a river. See \autoref{alg:check river intersection}. A bounding box intersection test between the edge defined by node translation and river edges can be performed to reduce the number of edge intersection tests required.

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/stalemate.png}
            \caption{A stalemate situation is when a node's translation path $ \nodeVectorCT $ (iteration 1) intersects a river $ \stalemateMax $ times. The node is translated back to its previous position (iteration 2). A stalemate often occurs when the area is congested and the node is unable to translate to a new position without intersecting a river.}
            \label{fig:stalemate}
        \end{figure}
    }
